The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-05-18 discussion.tex
修改文档的结构
明确各agent 的划分，设计meta agent
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点

% !TEX root = Eco-Model.tex
\section{Discussion} % (fold)
\label{sec:discussion}

% section discussion (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Contributions, Limitations, and Future Research} % (fold)
\label{sec:contributions_limitations_and_future_research}

On the other hand, it means, that even if many indicators for the collaboration perspectives are applied it has to be regarded that they will not be able to draw a complete and objective picture of the collaboration performance.
% section contributions_limitations_and_future_research (end)
